---
title: "Q1."
author: "Salman"
date: "2024-04-06"
output: word_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(did)
library(fixest)
library(bacondecomp)
library(ggplot2)
library(foreign)
library(haven)
library(dplyr)
library(tidyverse)
file_path <- "E:/job_displacement_data.dta"


data <- read_dta(file_path)

# Generate treatment dummy
data$treated <- ifelse(data$year >= data$group & data$group != 0, 1, 0)

# Two-way fixed effects model
twfe_model <- feols(income ~ treated | id + year, data = data)

# Print summary 
summary(twfe_model)

# Create interaction terms manually between 'treated' and 'year'
data$interaction <- interaction(data$treated, data$year)

# Estimating the model with interaction terms to see the effect over time
model_interaction <- feols(income ~ interaction + female + white + occ_score | id + year, data = data)

# Viewing the summary to interpret interaction effects
summary(model_interaction)

# Extract estimates and confidence intervals directly from the two-way fixed effects model
estimates <- coef(twfe_model)
cis <- confint(twfe_model)


# Adjust this part according to what you actually intend to plot
plot_data <- data.frame(
  id = names(estimates),
  estimate = estimates,
  ci_lower = cis[, 1],
  ci_upper = cis[, 2]
)

plot_data$id <- factor(plot_data$id, levels = unique(plot_data$id))

# Plotting
ggplot(plot_data, aes(x = id, y = estimate, group = 1)) +
  geom_line() +
  geom_point() +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), fill = "blue", alpha = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  scale_x_discrete(name = "ID") +
  ylab("Effect on Income") +
  ggtitle("Plot Title: Adjust Accordingly") +
  theme_minimal()


---
title: "Q2"
author: "Salman"
date: "2024-04-06"
output: word_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
library(did)
library(fixest)
library(bacondecomp)
library(ggplot2)
library(foreign)
library(haven)
library(dplyr)
library(tidyverse)
library(plm)

file_path <- "E:/job_displacement_data.dta"

data <- read_dta(file_path)

att_gt_out <- att_gt(
  yname = "income",  
  tname = "year",   
  idname = "id",     
  gname = "group",   
  data = data       
)

summary(att_gt_out)

print(att_gt_out$att)

att_gt_out <- att_gt(data = data, 
                     yname = "income",
                     tname = "year",    
                     idname = "id",     
                     gname = "group")

agg_effects <- aggte(att_gt_out, type = "dynamic")

str(agg_effects)

# Plotting
plot(agg_effects$egt, agg_effects$att.egt, type = "b", 
     xlab = "Event Time", ylab = "Estimated Treatment Effect",
     main = "Event Study Analysis", ylim = c(min(agg_effects$att.egt - agg_effects$se.egt*1.96), 
                                             max(agg_effects$att.egt + agg_effects$se.egt*1.96)))

# Add error bars
lower_bounds <- agg_effects$att.egt - 1.96 * agg_effects$se.egt
upper_bounds <- agg_effects$att.egt + 1.96 * agg_effects$se.egt

for(i in 1:length(agg_effects$egt)) {
  segments(agg_effects$egt[i], lower_bounds[i], agg_effects$egt[i], upper_bounds[i])
}


overall_effect <- aggte(att_gt_out, type = "simple")

print(overall_effect)


---
title: "Q3"
author: "Salman"
date: "2024-04-06"
output: word_document
---

```{r}

library(fixest)
library(ggplot2)
library(haven)
library(did)

file_path <- "E:/job_displacement_data.dta"

# Reading the dataset with haven
data <- read_dta(file_path)

# Adjusting for anticipated treatment effect
data$anticipated_treatment <- ifelse(data$year >= data$group - 1 & data$group > 0, 1, 0)

# Adjust the group variable for anticipation
data$group_anticipate <- ifelse(data$group > 0, data$group - 1, 0)

# Using att_gt from the did package
att_gt_out_anticipate <- att_gt(yname = "income", tname = "year", idname = "id", 
                                gname = "group_anticipate", data = data)

# Aggregate to get a simple overall treatment effect
overall_effect_anticipate <- aggte(att_gt_out_anticipate, type = "simple")
print(overall_effect_anticipate)

overall_att <- overall_effect_anticipate$overall.att
overall_se <- overall_effect_anticipate$overall.se

# Calculating the confidence interval
ci_lower <- overall_att - 1.96 * overall_se
ci_upper <- overall_att + 1.96 * overall_se

# Prepare data for plotting
plot_data <- data.frame(att = overall_att, ci_lower = ci_lower, ci_upper = ci_upper)

ggplot(plot_data, aes(x = factor(1), y = att)) +
  geom_col() +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  xlab("Overall Treatment Effect") + ylab("ATT") +
  ggtitle("Overall Treatment Effect with Confidence Interval") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())


---
title: "Q4"
author: "Salman"
date: "2024-04-06"
output: word_document
---

```{r}

library(did)
library(foreign)
library(haven)


#PART A

file_path <- "E:/job_displacement_data.dta"

data <- read_dta("E:/job_displacement_data.dta")


data$group_anticipate <- ifelse(data$group > 0, data$group - 1, 0)


att_gt_out <- att_gt(
  yname = "income",
  tname = "year",
  idname = "id",
  gname = "group_anticipate", 
  xformla = ~ female + white, 
  data = data,
  est_method = "dr"           
)


summary(att_gt_out)






# Extract the group-time ATTs from the att_gt object
group_time_atts <- att_gt_out$group.time.atts


att_1992_1992 <- group_time_atts[(group_time_atts$g == 1991) & (group_time_atts$t == 1992), ]

# Print out the ATT for the year 1992,1992 accounting for anticipation
print(att_1992_1992$att)




agg_effects <- aggte(att_gt_out, type = "dynamic")


plot(agg_effects$egt, agg_effects$att.egt, type = "b",
     xlab = "Event Time", ylab = "ATT",
     main = "Event Study Analysis with Anticipation and Covariates")

# Adding error bars
for (i in 1:length(agg_effects$egt)) {
  segments(agg_effects$egt[i], 
           agg_effects$att.egt[i] - 1.96 * agg_effects$se.egt[i], 
           agg_effects$egt[i], 
           agg_effects$att.egt[i] + 1.96 * agg_effects$se.egt[i])
}


#PART B

# Using the doubly robust approach including 'female' and 'white' as covariates
att_dr <- att_gt(
  data = data, 
  yname = "income", 
  tname = "year", 
  idname = "id", 
  gname = "group_anticipate", 
  xformla = ~ female + white,
  est_method = "dr"
)
summary(att_dr)

# Using the outcome regression approach
att_reg <- update(att_dr, est_method = "reg")
summary(att_reg)

# Using the inverse propensity score weighting approach
att_ipw <- update(att_dr, est_method = "ipw")
summary(att_ipw)



---
title: "Q5"
author: "Salman"
date: "2024-04-06"
output: word_document
---

```{r}
library(fixest)
library(ggplot2)
library(did)
library(haven)

file_path <- "E:/job_displacement_data.dta"
data <- read_dta(file_path)

data$treated <- ifelse(data$year >= data$group - 1 & data$group != 0, 1, 0)

model_twfe_occ <- feols(income ~ treated * occ_score | id + year, data = data)
summary(model_twfe_occ)

data$interaction_year <- interaction(data$treated, data$year)
data$interaction_occ_score <- data$treated * data$occ_score

model_interaction <- feols(income ~ interaction_year + interaction_occ_score + treated + occ_score | id + year, data = data)
summary(model_interaction)

estimates <- coef(model_interaction)
cis <- confint(model_interaction)

event_times <- names(estimates)[grepl("interaction_year", names(estimates))]

plot_data <- data.frame(
  time = as.numeric(gsub("interaction_year", "", event_times)),
  estimate = estimates[event_times],
  ci_lower = cis[event_times, 1],
  ci_upper = cis[event_times, 2]
)

plot_data$time <- factor(plot_data$time, levels = unique(plot_data$time))

ggplot(plot_data, aes(x = time, y = estimate, group = 1)) +
  geom_line() +
  geom_point() +
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), fill = "blue", alpha = 0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  scale_x_discrete(name = "Years Relative to Displacement") +
  ylab("Effect on Income with Occupation Score") +
  ggtitle("Event Study Plot: Impact of Job Displacement on Income") +
  theme_minimal()


